---
title: "o2r - Html test"
author: "Juan Sebastian Garzon Alvarado"
output: md_document
---

This documet contais some script that opens an ERC (see https://o2r.uni-muenster.de/#/) and measures how long it takes until the HTML-page has fininished [rendering](https://en.wikipedia.org/wiki/Front_end_and_back_end).

## Required libraries

```{r libraries}
library(RSelenium)
library(parallel)
library(binman)
```

## Function

The `visitERC` function opens an ERC and returns information about the backend performance and frontend performance. For a similar approach ussing python visit this [repository](https://github.com/chewitt-swts/GeicoAutoTest/blob/master/PageLoadTimeClass.py)

```{r visitERC}

#Function to visit an ERC (web) and extract information about rendering time

visitERC<-function(erc,portNumber){
  
  #Starting Selenium server
  available.versions<-list_versions("chromedriver")
  r<-rsDriver(port=portNumber,chromever=available.versions[[1]][1])
  remDr<-r[["client"]]
  
  # Navigating to webpage
  
  remDr$navigate(erc)
  
  # Extracting information
  navigationStart<-remDr$executeScript("return window.performance.timing.navigationStart")
  responseStart<-remDr$executeScript("return window.performance.timing.responseStart")
  domComplete<-remDr$executeScript("return window.performance.timing.domComplete")
  
  # Stoping server
  
  remDr$close()
  r[["server"]]$stop()
  result<-list(x=navigationStart,y=responseStart,z=domComplete)
  return(result)
}
```

## Test

For this test it is required to define the `ERC` link that is going to be rendered and the number of visits (`num_visits`) to perform. The number of simultaneous visits is limited to the number of CPU cores of your machine. This means that a machine with 2 cores would make at most 2 simultaneous visits. For a test with `N` visits (and 2 avaiblable cores) the test will perform `N/2` consecutive series of visits (2 simultaneous) until reaching that number. Visit this [link](https://nceas.github.io/oss-lessons/parallel-computing-in-r/parallel-computing-in-r.html) for more information about parallel computing in R.

The test information is recorded on the dataframe `df`.

```{r testing}

# Defining parameters
num_visits<-10
ERC<-"https://o2r.uni-muenster.de/ui/#/erc/BR5vo"

# Creating dataframe with link and port number (to avoid Selenium Server errors)

links<-replicate(num_visits,ERC)
df<-data.frame(Links=links)
df$port<-((4567:(4567+nrow(df)-1)))

# Applying function

results<-mcmapply(visitERC,df$Links,df$port)

# Adding information to dataframe

df$NavigationStart<-unlist(results[1,])
df$responseStart<-unlist(results[2,])
df$domComplete<-unlist(results[3,])

# Calculations
df['backendPerformance_calc']<- df$responseStar-df$NavigationStart
df['frontendPerformance_cal']<- df$domComplete-df$responseStart

print(df)
```

# TO DO
Add statistics / analysis (?)

