---
title: "HTML performance test of o2r user interface"
author: "Juan Sebastian Garzon Alvarado"
---

This document contains some script that opens an ERC (see https://o2r.uni-muenster.de/#/) and measures how long it takes until the HTML-page has fininished [rendering](https://en.wikipedia.org/wiki/Front_end_and_back_end).

## Required libraries

```{r libraries}
library("RSelenium")
library("parallel")
library("binman")
```

## Function

The `visitERC` function opens an ERC and returns information about the backend performance and frontend performance.
For a similar approach that informed this workflow using Python visit  [github.com/chewitt-swts/GeicoAutoTest](https://github.com/chewitt-swts/GeicoAutoTest/blob/master/PageLoadTimeClass.py).

```{r visitERC}
#Function to visit an ERC (web) and extract information about rendering time
visitERC <- function(erc, portNumber){
  
  #Starting Selenium server
  available.versions <- binman::list_versions("chromedriver")
  r <- rsDriver(port=portNumber,chromever=available.versions[[1]][1])
  remDr <- r[["client"]]
  
  # Navigating to webpage
  remDr$navigate(erc)
  
  # Extracting information
  navigationStart <- remDr$executeScript("return window.performance.timing.navigationStart")
  responseStart <- remDr$executeScript("return window.performance.timing.responseStart")
  domComplete <- remDr$executeScript("return window.performance.timing.domComplete")
  
  # Stopping server
  remDr$close()
  r[["server"]]$stop()
  result <- list(x = navigationStart, y = responseStart, z = domComplete)
  return(result)
}
```

## Test

For this test it is required to define the `ERC_url` link that is going to be rendered and the number of visits (`num_visits`) to perform.
The number of simultaneous visits is limited to the number of CPU cores of your machine.
This means that a machine with 2 cores would make at most 2 simultaneous visits.
For a test with `N` visits (and 2 available cores) the test will perform `N/2` consecutive series of visits (2 simultaneous) until reaching that number.
Visit [this link](https://nceas.github.io/oss-lessons/parallel-computing-in-r/parallel-computing-in-r.html) for more information about parallel computing in R.

The test information is recorded on the dataframe `df`.

```{r testing}
# Defining parameters
num_visits <- 10
ERC_url <- "https://o2r.uni-muenster.de/ui/#/erc/BR5vo"

# Creating dataframe with link and port number (to avoid Selenium Server errors)
links <- replicate(num_visits, ERC_url)
df <- data.frame(links = links)
df$port<-((4567:(4567+nrow(df)-1)))

# Applying function
results <- mcmapply(FUN = visitERC, df$links, df$port)

# Adding information to dataframe
df$NavigationStart <- unlist(results[1,])
df$responseStart <- unlist(results[2,])
df$domComplete <- unlist(results[3,])

# Calculations
df['backendPerformance_calc'] <- df$responseStar - df$NavigationStart
df['frontendPerformance_cal'] <- df$domComplete - df$responseStart

print(df)
```

# TO DO

- Add statistics / analysis
