---
title: "LoadTest"
author: "Sebastian Garzon"
output: html_document
---

This documet contais some script to test the o2r API endpoint using the `loadtest` [library](https://github.com/tmobile/loadtest).

## Required libraries
```{r libs}
library("loadtest")
library("ggplot2")
```

## Other requirements

In order to use the `loadtest` library it is required to install Java and Jmeter. Other requirements are described on the [installation document](https://github.com/tmobile/loadtest#installation) of this library.

## Preparation

This documet contais some script to test the o2r API.

**Note:** This document is best run chunk by chunk, and not as a whole, using RStudio.
`loadtest` library requires the path to the jmeter bin folder to work. You can add a file `.Renviron` on your local machine next to this file, and it define the path in the environment variable "LOADTEST_JMETER_PATH". For more information about this local variable refer to this [guide](https://github.com/tmobile/loadtest#installing-jmeter).

```{r  cache=TRUE,message=FALSE}

#Building DataSets

#Configuration required to use 'loadtest' library, this system variable is stored in a .Renviron file. LOADTEST_JMETER_PATH="[path to jmeter bin folder]"
Sys.getenv("LOADTEST_JMETER_PATH")

```
# Test 

## LoadTest o2r API entry point

The purpose of this test is to evaluate the performance of the o2r API entry point during a period of time of approximately 3 minutes receiving requests from different users (Threads).  

```{r dataProcess, cache=TRUE,message=FALSE}

#List with number of Threads for the test
test_threads<-c(1,2,3,4,5,6,7,8)

#List with the number of loops for each test scenario (per Thread). These numbers are an estimation for a 3 minute test for every configuration scenario. Less Threads require more individual loops per thread in order to extend the test to 3 minutes.

number_loops<-c(28500,27000,25000,23000,20000,17500,15000,14000)

# Run multiple tests

test_variables  <- paste("Test_threads_",test_threads,sep="")
test_functions<-paste0('loadtest(url = "https://o2r.uni-muenster.de/api/v1", method = "GET", threads =',test_threads,', loops=',number_loops,')')
eq<-paste(paste(test_variables,test_functions,sep="<-"),collapse = ";")
eval(parse(text=eq))

#Save image of the current R environment

save.image(file='datasets.RData')
```

## Including Plots

## Time to complete request over duration of test

The elapsed time of each request of the course of the test.

```{r}

ListTest<-ls()
ListTest<-ListTest[substring(ListTest,1,5)=="Test_"]

plot_elapsed_times_o2r<-function(i){

   plot_test<-eval(as.name(i))
   plot<-plot_elapsed_times(plot_test)+scale_color_manual(values=c("#606060", "#004288"), drop=FALSE)+labs(title=paste0("Time to complete request (milliseconds) for ", max(plot_test$threads)," thread(s)"))
   return(print(plot))
}

for (f in ListTest){
  plot_elapsed_times_o2r(f)
 }

```

## Distribution of time to complete responses

A histogram of the elapsed times

```{r}
ListTest<-ls()
ListTest<-ListTest[substring(ListTest,1,5)=="Test_"]

plot_elapsed_times_histogram_o2r<-function(i){
   plot_test<-eval(as.name(i))
   plot<-plot_elapsed_times_histogram(plot_test)+scale_fill_manual(values=c("#606060", "#004288"), drop=FALSE)+
    labs(title=paste0("Time to complete response (milliseconds) for ", max(plot_test$threads)," thread(s)"))
}

for (f in ListTest){
  plot_elapsed_times_histogram_o2r(f)
 }

```
