---
title: "LoadTest"
author: "Sebastian Garzon"
output: md_document
---

This documet contais some script to test the o2r API endpoint using the `loadtest` [library](https://github.com/tmobile/loadtest).

## Required libraries
```{r libs}
library("loadtest")
library("ggplot2")
library("dplyr")
library("tidyr")
```

## Other requirements

In order to use the `loadtest` library it is required to install Java and Jmeter. Other requirements are described on the [installation document](https://github.com/tmobile/loadtest#installation) of this library.

## Preparation

This documet contais some script to test the o2r API.

**Note:** This document is best run chunk by chunk, and not as a whole, using RStudio.
`loadtest` library requires the path to the jmeter bin folder to work. You can add a file `.Renviron` on your local machine next to this file, and it define the path in the environment variable "LOADTEST_JMETER_PATH". For more information about this local variable refer to this [guide](https://github.com/tmobile/loadtest#installing-jmeter).

```{r  cache=TRUE,message=FALSE}

#Building DataSets

#Configuration required to use 'loadtest' library, this system variable is stored in a .Renviron file. LOADTEST_JMETER_PATH="[path to jmeter bin folder]"

#Sys.getenv("LOADTEST_JMETER_PATH")

```
# Test 

## LoadTest o2r API entry point

The purpose of this test is to evaluate the performance of the o2r API entry point simulating users making multiple request simultaneously. Every test is going to be defined by a number of users (Threads) and the number of requests per user (same number for every user). The `test_threads` list define the number of users for test and `request_num` the number of request per user. For example with `test_threads = c(1,2)` and `request_num =500` there are going to be 2 tests, the first with one thread of 500 requests and the second one with two threads of 500 requests per thread (i.e., 1000 request in total).

```{r dataProcess, eval=FALSE, cache=TRUE,message=FALSE}

# Define test
test_threads<-c(1,2,3,4,5,6)
# Define individual number of request
request_num<-2000

# List with the number of loops for each test scenario (per Thread). 

number_loops<-rep.int(request_num,length(test_threads))

# Run multiple consecutive tests

test_variables  <- paste("Test_threads_",test_threads,sep="")
test_functions<-paste0('loadtest(url = "https://o2r.uni-muenster.de/api/v1", method = "GET", threads =',test_threads,', loops=',number_loops,')')
eq<-paste(paste(test_variables,test_functions,sep="<-"),collapse = ";")
eval(parse(text=eq))

#Save image of the current R environment

save.image(file='datasets.RData')
```

# Results

## Time to complete request over duration of test

The elapsed time of each request of the course of the test.

```{r elapsedTime, message=FALSE}
#Loading results

load('datasets.Rdata')

# Extracting variable names that correspond to Tests

ListTest<-ls()
ListTest<-ListTest[substring(ListTest,1,5)=="Test_"]

# Plot function of elapsed times 

plot_elapsed_times_o2r<-function(i){
   plot_test<-eval(as.name(i))
   plot<-plot_elapsed_times(plot_test)+scale_color_manual(values=c("#606060", "#004288"), drop=FALSE)+labs(title=paste0("Time to complete request (milliseconds) for ", max(plot_test$threads)," thread(s)"))
   return(print(plot))
}

# One plot per test

for (f in ListTest){
  plot_elapsed_times_o2r(f)
 }

```

## Distribution of time to complete responses

A histogram of the elapsed times

```{r histogram, message=FALSE}

# Plot function of elapsed times histogram

plot_elapsed_times_histogram_o2r<-function(i){
   plot_test<-eval(as.name(i))
   
   plot<- plot_elapsed_times_histogram(plot_test)+scale_fill_manual(values=c("#606060", "#004288"), drop=FALSE)+labs(title=paste0("Time to complete response (milliseconds) for ", max(plot_test$threads)," thread(s)"))
   
   return(print(plot))
}

# One histogram plot per test
for (test in ListTest){
   plot_elapsed_times_histogram_o2r(test)
 }

```
## TO DO:

More meaninful plots of the test:

* Average time vs number of threads
* Average Fail request vs number of threads
